Type-Safe Client-Server Communication in Web Applications

### 2014-02-27 paper.tex
Add Conclusion section, so I dont forget that part later.
Put Jen's Javascript in a figure instead of inline. So pretty!

To put this all into perspective, let's take a look at the completely fictious
case of Jen, a software developer tasked with implementing a simple ``chatbox''
for a client's web site. Jen is a senior developer, but has no previous
experience with web applications. She is, however, a competend engineer and a
fast learner, and so manages to produce the following piece of client-side code.

\begin{code}
function handshake(sock) {sock.send('helo');}
function chat(sock, msg) {sock.send('text' + msg);}

@@

    sock.onopen = function(e) {
        handshake(sock);
        msgbox.addEventListener('keydown', function(e) {
            if(e.keyCode == 13) {
                var msg = msgbox.value;
                msgbox.value = '';
            }
        });
    };
};
\end{code}

@@

The code looks solid enough, but Jen is not happy. This simple piece of code
contains no less than three asynchronous callbacks, making the program flow
non-obvious. Moreover, she is concerned about the network communication. The
protocol will clearly need to be redesigned if the application is to be
upgraded with new features later, but the client is not willing to pay Jen to
spend development time on features he has not requested and perhaps never will.
If the protocol will need to be updated in the future, how much time will Jen
need to spend on ensuring that all code using the network protocol stays
updated? Then there is the server component to think; of how much extra work
will it take to ensure that the two code bases stay in sync? Coming from a
desktop background, Jen wonders why something so seemingly simple should
involve client/server architectures and network protocols at all.

@@

>>>>

To put this all into perspective, let's take a look at the completely fictious
case of Jen, a software developer tasked with implementing a simple ``chatbox''
for a client's web site. Jen is a senior developer, but has no previous
experience with web applications. She is, however, a competend engineer and a
fast learner, and so manages to produce the following client-side code in
figure \ref{lst:javascript-client}.

\begin{listingfloat}
\begin{code}
function handshake(sock) {sock.send('helo');}
function chat(sock, msg) {sock.send('text' + msg);}

@@

  sock.onopen = function(e) {
    handshake(sock);
    msgbox.addEventListener('keydown', function(e) {
      if(e.keyCode == 13) {
        var msg = msgbox.value;
        msgbox.value = '';
        chat(msg);
      }
    });
  };
};
\end{code}
\caption{Javascript chatbox implementation}
\label{lst:javascript-client}
\end{listingfloat}

@@

The code looks solid enough, but Jen is not happy. This simple piece of code
contains no less than three asynchronous callbacks, making the program flow
non-obvious. Moreover, she is concerned about the network communication. The
protocol will clearly need to be redesigned if the application is to be
enhanced with new features later, but the client is not willing to pay Jen to
spend development time on features he has not requested and perhaps never will.

If the protocol will need to be updated in the future, how much time will Jen
need to spend on ensuring that all code using the network protocol stays
updated? Then there is the server component to think of; how much extra work
will it take to ensure that the two code bases stay in sync? How much code
will need to be written twice, one version for the client and one for the
server, due to the unfortunate fact that the two can't share any code?

Coming from a desktop background, Jen wonders why something so seemingly simple
should involve client/server architectures and network protocols at all.

@@

\section{Conclusion}
